---
title: "Event Categories"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r, message = FALSE, echo=FALSE}
library(tidyverse)
library(dbplyr)
library(rvest)
library(plotly)
```

### Data Tidying
```{r, message = FALSE, echo = FALSE}
park_event = read.csv("./park_events.csv") %>% 
  select(event_id, title, date,start_time, end_time, cost_free, must_see)
park_location = read.csv("./park_location.csv") %>% 
  select(event_id, name, park_id, lat, long, borough)

park_1 = left_join (park_event, park_location, by = "event_id") 
 
park_organizer = read.csv("./park_organizer.csv")
park_cate = read.csv ("./park_cate.csv") %>% 
  rename(cate_name = name)

park_2  = left_join (park_cate, park_organizer, by = "event_id")


park_df = left_join (park_1, park_2,  by = "event_id")

```
After data processing and cleaning, there are 252,768 rows and 14 variables. 



### Popular categories
```{r, message = FALSE, echo=FALSE}
park_df %>% 
  separate(date, into = c("day","month", "year"), sep = "/") %>% 
  group_by(cate_name) %>% 
  summarize(count = n()) %>% 
  filter(count > 1000) %>% 
  mutate(cate_name = as.factor(cate_name)) %>% 
  mutate(cate_name = fct_reorder(cate_name, count)) %>% 
  ggplot(aes(x = cate_name, y = count)) + 
    geom_point() + 
    labs(
    title = "Park Event Category",
    x = "Event Categories",
    y = "Count"
  ) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1))
```
Based on the plot, top five event categories (with highest counts) are `Best for Kids`, `Fitness`, `Nature`, `Education`, `Art`. Five event categories (with lowest counts) are `My Summer House NYC`, `Shape Up New York`, `Summer Sports Expereince`, `Wildlife`, `GreemThumb Partner Events`. 

### Most popular categories distribution by location
```{r, message = FALSE, echo = FALSE}
popular_cate = park_df %>% 
  filter(cate_name %in% c("Best for Kids", "Fitness", "Art", "Nature", "Education")) %>% 

  plot_ly(
    x = ~lat, y = ~long, type = "scatter", mode = "markers", color = ~cate_name
   )
popular_cate
  
```
This plot shows the distribution of the top five event categories (`Best for Kids`, `Fitness`, `Nature`, `Education`, `Art`) with specific latitudes and longitude of each locations. 

### Most popular categories change by each year
```{r, message = FALSE, echo = FALSE}
park_df %>% 
  separate(date, into = c("day","month", "year"), sep = "/") %>% 
  filter(cate_name %in% c("Best for Kids", "Fitness", "Art", "Nature", "Education")) %>% 
  group_by(year,cate_name) %>% 
  summarize(count = n()) %>% 
  pivot_wider(
    names_from = year,
    values_from = count
  ) %>% 
  knitr::kable()
```
### 5 most popular categories.

To be more specific, we pick up 5 most held types of events in New York throughout the years. 

```{r, echo=FALSE}
park_df %>% 
  select(cate_name) %>% 
  group_by(cate_name) %>% 
  summarize(count = n()) %>% 
  arrange(desc(count)) %>% 
  head(5) %>% 
  knitr::kable()

```

From this table, we can see that "Best for kids" is the most popular category in New York City. It seems that people love to bring their kids to park events to relax. To find out the exact 5 most popular categories, we created a barplot showing the top 5 category distribution in each borough. 


```{r, echo=FALSE, message=FALSE}
## Most popular categories
B_df = 
  park_df %>% 
  group_by(borough, cate_name) %>% 
  summarize(count = n()) %>% 
  filter(borough == "B") %>% 
  arrange(desc(count)) %>% 
  head(5)

M_df = 
  park_df %>% 
  group_by(borough, cate_name) %>% 
  summarize(count = n()) %>% 
  filter(borough == "M") %>% 
  arrange(desc(count)) %>% 
  head(5)

Q_df = 
  park_df %>% 
  group_by(borough, cate_name) %>% 
  summarize(count = n()) %>% 
  filter(borough == "Q") %>% 
  arrange(desc(count)) %>% 
  head(5) 

R_df = 
  park_df %>% 
  group_by(borough, cate_name) %>% 
  summarize(count = n()) %>% 
  filter(borough == "R") %>% 
  arrange(desc(count)) %>% 
  head(5)

X_df = 
  park_df %>% 
  group_by(borough, cate_name) %>% 
  summarize(count = n()) %>% 
  filter(borough == "X") %>% 
  arrange(desc(count)) %>% 
  head(5)

first_df = rbind(M_df, B_df)
second_df = rbind(Q_df, R_df)
third_df = rbind(first_df, second_df)
whole_df = rbind(third_df, X_df)

whole_df %>% 
  mutate(borough = recode(borough, B = "Brooklyn", M = "Manhattan", Q = "Queens", R = "State Island", X = "Bronx")) %>% 
  ggplot(aes(x = borough, y = count, fill = cate_name)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(title = "Most Popular Categories") +
  coord_flip()
```

Although Manhattan is the smallest borough, it is the most densely populated, so it is no surprise that Manhattan had the most events. The top 5 categories were fitness, nature, volunteer, best for kids and tours. The most popular categories in other boroughs were similar to those of Manhattan. However, art & crafts park events were higher in the popularity rank compared to their counterparts in Bronx, Queens, and Staten Island.




