---
title: "'Good' and 'Free'"
output: 
  html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(dbplyr)
library(rvest)
library(plotly)
```



```{r, include=FALSE}

park_event = read.csv("./park_events.csv") %>% 
  select(event_id, title, date,start_time, end_time, cost_free, must_see)
park_location = read.csv("./park_location.csv") %>% 
  select(event_id, name, park_id, lat, long, borough)

park_1 = left_join(park_event, park_location, by = "event_id") 
 
park_organizer = read.csv("./park_organizer.csv")
park_cate = read.csv("./park_cate.csv") %>% 
  rename(cate_name = name)

park_2  = left_join (park_cate, park_organizer, by = "event_id")


park_df = left_join (park_1, park_2,  by = "event_id")


```

### Must-see Events
A good park event can be seen from the must see indicator. We want to show people who are interested in the park event which area contains the most park events worth participating in.

```{r, echo=FALSE, message=FALSE}
## Most popular events
mustsee_df =
  park_df %>% 
  select(borough, must_see) %>% 
  filter(must_see == "1") %>% 
  mutate(borough = recode(borough, B = "Brooklyn", M = "Manhattan", Q = "Queens", R = "State Island", X = "Bronx")) %>%
  group_by(borough) %>% 
  summarize(count = n()) %>% 
  arrange(desc(count)) %>% 
  head(5)

mustsee_df %>% 
  knitr::kable()

mustsee_df %>% 
  ggplot(aes(x = borough, y = count)) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(title = "Must-see Events")
```

Obviously, Manhattan had the most must-see events given its world-renowned reputation and its numerous and diverse park events. 

### Free Events
```{r, echo=FALSE, message=FALSE}
costfree_df =
  park_df %>% 
  select(borough, cost_free) %>% 
  filter(cost_free == "1") %>% 
  mutate(borough = recode(borough, B = "Brooklyn", M = "Manhattan", Q = "Queens", R = "State Island", X = "Bronx")) %>%
  group_by(borough) %>% 
  summarize(count = n()) %>% 
  arrange(desc(count)) %>% 
  head(5)

noncostfree_df = 
  park_df %>% 
  select(borough, cost_free) %>% 
  filter(cost_free == "0") %>%  
  mutate(borough = recode(borough, B = "Brooklyn", M = "Manhattan", Q = "Queens", R = "State Island", X = "Bronx")) %>%
  group_by(borough) %>% 
  summarize(count = n()) %>% 
  arrange(desc(count)) %>% 
  head(5)

cost_df = left_join(costfree_df, noncostfree_df, by = "borough")

cost_df %>% 
  ggplot(aes(x = borough, y = count.x / (count.x + count.y))) +
  geom_bar(stat = "identity", position = "dodge") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(title = "Proportions of Free Park Events",
  y = "Cost free / Total",
  x = "Borough")
```

We can see that Manhattan, Brooklyn, and Staten Island had the most free park events. In fact, nearly 90% of all three boroughs' park events were free. To sum up, visiting parks in Manhattan is the most cost-effective, as it had the highest number and diversity of parks as well as the highest ratio of free park events. 
